Lab 2 Final Report: COVID-19 Case Rate vs Population Demographics and Mask Policy

### 2020-12-06 Jackson_Liu_Temlock_Zhang_Lab2_Draft_Report.Rmd
Update Jackson_Liu_Temlock_Zhang_Lab2_Draft_Report.Rmd
update model 3

Next, the regression model for model 3 is created based on the existing work from model 2. Two additional variables discussed in Model 3 will be introduced as maximalist approach. The first variable is the "mask_public_bool" (whether the state enforced public mask mandate or not) that represents the policy effects. The second variable introduced is "population_density" (the value is logged as discussed earlier) which is considered an important factor related to the spread of disease.

@@

According to the plot of Homoskedasticity, the standardized residual falls into a reasonable range and the line looks smooth without concerning skews. There is no significant evidence that the model violates homoskedasticity assumptions.
```{r}

@@

@@

In conclusion, we see that although the population demographics had varying effects on the COVID-19 case rate, the greatest effect was seen from the mask policy. Going back to our original question, it can be suggested within the data that the effect of a mask-related policy is something that should not be neglected in comparison to the population demographics. Therefore, it seems that the COVID-19 case rate at the state-level is dependent on masks, and that ultimately, there are effective policy and control measures that can be taken by state governments that have some contribution towards combating it's spread relative to factors that cannot be controlled. However, it should be noted that these insights are qualified by the assumptions and limitations laid out throughout the report, namely that there are potential issues in meeting the IID assumption and that there is explanatory information that is lost from both the variables investigated as well as the those that were not included in the dataset.

>>>>

Next, the regression model for model 3 is created based on the existing work from model 2. Two additional variables discussed in Model 3 will be introduced as the maximalist approach. The first variable is the "mask_public_bool" (whether the state enforced public mask mandate or not) that represents the policy effects. The second variable introduced is "population_density" (the variable is transformed with log of 10 as discussed earlier) which is considered an important factor related to the spread of disease.

@@

According to the plot of Homoskedasticity, the standardized residual falls into a reasonable range and the curve looks smooth without concerning skews. There is no significant evidence that the model violates homoskedasticity assumptions.
```{r}

@@

```
Additionally, a Breusch-Pagan test is run to check the level of heteroskedasticity. The test result shows it fails to reject the null hypothesis, which indicates that there is no strong evidence of heteroskedasticity in model 3.

```{r, echo=FALSE}
bptest(model3)
```

@@

In conclusion, we see that although the population demographics had varying effects on the COVID-19 case rate, the greatest effect was seen from the mask policy. Going back to our original question, it can be suggested within the data that the effect of a mask-related policy is something that should not be neglected in comparison to the population demographics. Therefore, it seems that the COVID-19 case rate at the state-level is dependent on masks, and that ultimately, there are effective policy and control measures that can be taken by state governments that have some contribution towards combating its spread relative to factors that cannot be controlled. However, it should be noted that these insights are qualified by the assumptions and limitations laid out throughout the report, namely that there are potential issues in meeting the IID assumption and that there is explanatory information that is lost from both the variables investigated as well as the those that were not included in the dataset.
